---
title: "LAB7"
author: "michael hogsett"
date: "10/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1




## Task 2
plot 1
```{r}
mychisim<-function(n1=10,sigma1=4,mean1=10,iter=1000,ymax=0.15,x=20, y=0.1){ 
  
  y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

ssq1=apply(data1.mat,2,var) # ssq1 is s squared

w=(n1-1)*ssq1/sigma1^2      #chi-sq stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]-1)*s^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}

mychisim(iter=1000,ymax=0.15)



```



plot 2
```{r}
mychisim<-function(n1=20,sigma1=4,mean1=10,iter=1000,ymax=0.15,x=40, y=0.1){ 
  
  y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

ssq1=apply(data1.mat,2,var) # ssq1 is s squared

w=(n1-1)*ssq1/sigma1^2      #chi-sq stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]-1)*s^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}

mychisim(iter=1000,ymax=0.1)



```
plot 3

```{r}
mychisim<-function(n1=100,sigma1=4,mean1=10,iter=1000,ymax=0.15,x=130, y=0.061){ 
  
  y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

ssq1=apply(data1.mat,2,var) # ssq1 is s squared

w=(n1-1)*ssq1/sigma1^2      #chi-sq stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]-1)*s^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}

mychisim(iter=1000,ymax=0.1)



```

plot 4

```{r}
mychisim<-function(n1=200,sigma1=4,mean1=10,iter=1000,ymax=0.15,x=259, y=0.03){ 
  
  y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

ssq1=apply(data1.mat,2,var) # ssq1 is s squared

w=(n1-1)*ssq1/sigma1^2      #chi-sq stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]-1)*s^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}

mychisim(iter=1000,ymax=0.04)



```


Make a histogram of chisq$w.
```{r}

mychisim<-function(n1=10,sigma1=10,mean1=20,iter=1500,ymax=0.1,...){    # adjust ymax to make graph fit
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

ssq1=apply(data1.mat,2,var) # ssq1 is s squared

w=(n1-1)*ssq1/sigma1^2      #chi-sq stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]-1)*s^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(locator(1),c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
return(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}
windows()
chisq=mychisim(iter=1500,ymax=0.15)

hist(chisq$w)

```
## Task 3
plot 1: n1 = 10
```{r}

#Make plot according to the following option of values stated in function 

myTsim<-function(n1=10,sigma1=4,mean1=10,iter=1000,ymax=0.1,x=2,y=0.3,...){    # adjust ymax to make graph fit
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

sd1=apply(data1.mat,2,sd) # sd
ybar=apply(data1.mat,2,mean)  # mean

w=(ybar-mean1)/(sd1/sqrt(n1))      #T stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",T," iterations= ",iter)),
xlab=expression(paste(T, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(y)-mu),s/sqrt(n1))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="T")) # some output to use if needed
}
myTsim(iter=1000,ymax=0.45)
```

plot 2: n1 = 20
```{r}

#Make plot according to the following option of values stated in function 

myTsim<-function(n1=20,sigma1=4,mean1=10,iter=1000,ymax=0.1,x=2,y=0.3,...){    # adjust ymax to make graph fit
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

sd1=apply(data1.mat,2,sd) # sd
ybar=apply(data1.mat,2,mean)  # mean

w=(ybar-mean1)/(sd1/sqrt(n1))      #T stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",T," iterations= ",iter)),
xlab=expression(paste(T, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(y)-mu),s/sqrt(n1))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="T")) # some output to use if needed
}
myTsim(iter=1000,ymax=0.45)


```

plot 3: n1 = 100
```{r}
#Make plot according to the following option of values stated in function 

myTsim<-function(n1=100,sigma1=4,mean1=10,iter=1000,ymax=0.1,x=2,y=0.3,...){    # adjust ymax to make graph fit
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

sd1=apply(data1.mat,2,sd) # sd
ybar=apply(data1.mat,2,mean)  # mean

w=(ybar-mean1)/(sd1/sqrt(n1))      #T stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",T," iterations= ",iter)),
xlab=expression(paste(T, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(y)-mu),s/sqrt(n1))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="T")) # some output to use if needed
}
myTsim(iter=1000,ymax=0.45)
```
plot 4: n1=200
```{r}
#Make plot according to the following option of values stated in function 

myTsim<-function(n1=200,sigma1=4,mean1=10,iter=1000,ymax=0.1,x=2,y=0.3,...){    # adjust ymax to make graph fit
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

sd1=apply(data1.mat,2,sd) # sd
ybar=apply(data1.mat,2,mean)  # mean

w=(ybar-mean1)/(sd1/sqrt(n1))      #T stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",T," iterations= ",iter)),
xlab=expression(paste(T, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(y)-mu),s/sqrt(n1))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="T")) # some output to use if needed
}
myTsim(iter=1000,ymax=0.45)
```


```{r}
#Invoke the function with n_1=10,iter=1500,μ_1=20,σ_1=10 and place the output into an object called T. Make a histogram of T$w.

myTsim<-function(n1=10,sigma1=10,mean1=20,iter=1500,ymax=0.1,x=2,y=0.3,...){    # adjust ymax to make graph fit
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1

data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1

sd1=apply(data1.mat,2,sd) # sd
ybar=apply(data1.mat,2,mean)  # mean

w=(ybar-mean1)/(sd1/sqrt(n1))      #T stat

hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]," = ",n1," statistic = ",T," iterations= ",iter)),
xlab=expression(paste(T, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1-1),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(y)-mu),s/sqrt(n1))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="T")) # some output to use if needed
}
T<-myTsim(iter=1500,ymax=0.45)

hist(T$w)

```

## Task 4

Plot 1:
o	Use mychisim2() to sample from two normal populations with the following parameters: 	n_1=10,n_2=10,μ_1=5,μ_2=10,σ_1=σ_2=4,iter=1000
```{r}

#n_1=10,n_2=10,μ_1=5,μ_2=10,σ_1=σ_2=4,iter=1000
mychisim2<-function(n1=10,n2=10,sigma1=4,sigma2=4,mean1=5,mean2=10,iter=1000,ymax=0.07,x=30,y=0.04,...){ y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=(n1+n2-2)*spsq/(sigma1^2)#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]+n[2]-2)*S[p]^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}

mychisim2(iter=1000, ymax = 0.08)



```
Plot 2: 
	n_1=20,n_2=10,μ_1=3,μ_2=5,σ_1=σ_2=10,iter=1000
```{r}
#n_1=10,n_2=10,μ_1=5,μ_2=10,σ_1=σ_2=4,iter=1000
mychisim2<-function(n1=20,n2=10,sigma1=3,sigma2=5,mean1=10,mean2=10,iter=1000,ymax=0.07,x=80, y=0.04,...){ y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=(n1+n2-2)*spsq/(sigma1^2)#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]+n[2]-2)*S[p]^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}

mychisim2(iter=1000, ymax = 0.08)




```
	
	Plot 3
		n_1=50,n_2=50,μ_1=5,μ_2=10,σ_1=σ_2=4,iter=10000
```{r}
mychisim2<-function(n1=50,n2=50,sigma1=4,sigma2=4,mean1=5,mean2=10,iter=10000,ymax=0.07,x=140,y=0.04,...){ y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=(n1+n2-2)*spsq/(sigma1^2)#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]+n[2]-2)*S[p]^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}

mychisim2(iter=10000, ymax = 0.05)


```
	Plot 4:
	
				n_1=80,n_2=50,μ_1=3,μ_2=5,σ_1=σ_2=10,iter=10000
```{r}
mychisim2<-function(n1=80,n2=50,sigma1=10,sigma2=10,mean1=3,mean2=5,iter=10000,ymax=0.07,x=160,y=0.04,...){ y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=(n1+n2-2)*spsq/(sigma1^2)#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]+n[2]-2)*S[p]^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}

mychisim2(iter=1000, ymax = 0.06)


```
	
	
	Use default values in the function with iter=10000 and use the output to make a histogram as before.

```{r}

mychisim2<-function(n1=10,n2=14,sigma1=3,sigma2=3,mean1=5,mean2=10,iter=10000,ymax=0.07,x=40,y=0.04,...){    # adjust ymax to make graph fit
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=(n1+n2-2)*spsq/(sigma1^2)#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",chi^2)),
xlab=expression(paste(chi^2, "Statistic",sep=" ")), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dchisq(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(chi^2==frac((n[1]+n[2]-2)*S[p]^2,sigma^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) # Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="Chi-sq")) # some output to use if needed
}

T<-mychisim2(iter=10000)
hist(T$w)
```

## Task 5
o	Alter the function myTsim2() to place the legend where you click with the mouse.
```{r}

myTsim2<-function(n1=10,n2=14,sigma1=3,sigma2=3,mean1=5,mean2=10,iter=1000,ymax=0.5,x=2,y=0.4,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ybar1= apply(data1.mat,2,mean)
ssq2=apply(data2.mat,2,var)
ybar2=apply(data2.mat,2,mean)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=((ybar1-ybar2)-(mean1-mean2))/sqrt(spsq*(1/n1+1/n2))#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",T)),
xlab=paste(" T Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(Y)[1]-bar(Y)[2])-(mu[1]-mu[2]),S[p]*sqrt(frac(1,n[1])+frac(1,n[2])))) #mathematical annotation -see ?plotmath

legend(locator(1),c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title) 
invisible(list(w=w,summary=summary(w),sdw=sd(w),fun="T")) # some output to use if needed
}
windows()
myTsim2(iter=10000)

```

$$

T = \frac {(\bar Y_{1}- \bar Y_{2}) - (\mu_{1}-\mu_{2})} {S_{p}\sqrt{1/n_{1}+1/n_2}}

$$
Y bar and S^2 represent the mean and variance of a random sample of n observations from a normally distributed population with mean mu and the variance sigma. Y bar and S^2 can be shown to be statistically independent when population had a normal distribution. (277)

	Use myTsim2() to sample from two normal populations with the following parameters:
	n_1=10,n_2=10,μ_1=5,μ_2=10,σ_1=σ_2=4,iter=1000
	n_1=20,n_2=10,μ_1=3,μ_2=5,σ_1=σ_2=10,iter=1000
	n_1=50,n_2=50,μ_1=5,μ_2=10,σ_1=σ_2=4,iter=10000
	n_1=80,n_2=50,μ_1=3,μ_2=5,σ_1=σ_2=10,iter=10000

PLot 1
```{r}
myTsim2<-function(n1=10,n2=10,sigma1=4,sigma2=4,mean1=5,mean2=10,iter=1000,ymax=0.5,x=1.5,y=0.4,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ybar1= apply(data1.mat,2,mean)
ssq2=apply(data2.mat,2,var)
ybar2=apply(data2.mat,2,mean)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=((ybar1-ybar2)-(mean1-mean2))/sqrt(spsq*(1/n1+1/n2))#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",T)),
xlab=paste(" T Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(Y)[1]-bar(Y)[2])-(mu[1]-mu[2]),S[p]*sqrt(frac(1,n[1])+frac(1,n[2])))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sdw=sd(w),fun="T")) # some output to use if needed
}
myTsim2(iter=1000)
```
Plot 2

```{r}

myTsim2<-function(n1=20,n2=10,sigma1=10,sigma2=10,mean1=3,mean2=5,iter=1000,ymax=0.5,x=1.5,y=0.4,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ybar1= apply(data1.mat,2,mean)
ssq2=apply(data2.mat,2,var)
ybar2=apply(data2.mat,2,mean)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=((ybar1-ybar2)-(mean1-mean2))/sqrt(spsq*(1/n1+1/n2))#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",T)),
xlab=paste(" T Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(Y)[1]-bar(Y)[2])-(mu[1]-mu[2]),S[p]*sqrt(frac(1,n[1])+frac(1,n[2])))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sdw=sd(w),fun="T")) # some output to use if needed
}
myTsim2(iter=1000)
```

Plot 3

```{r}

myTsim2<-function(n1=50,n2=50,sigma1=4,sigma2=4,mean1=5,mean2=10,iter=10000,ymax=0.5,x=1.5,y=0.4,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ybar1= apply(data1.mat,2,mean)
ssq2=apply(data2.mat,2,var)
ybar2=apply(data2.mat,2,mean)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=((ybar1-ybar2)-(mean1-mean2))/sqrt(spsq*(1/n1+1/n2))#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",T)),
xlab=paste(" T Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(Y)[1]-bar(Y)[2])-(mu[1]-mu[2]),S[p]*sqrt(frac(1,n[1])+frac(1,n[2])))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sdw=sd(w),fun="T")) # some output to use if needed
}
myTsim2(iter=10000)
```
Plot 4
```{r}

myTsim2<-function(n1=80,n2=50,sigma1=10,sigma2=10,mean1=3,mean2=5,iter=10000,ymax=0.5,x=1.5,y=0.4,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ybar1= apply(data1.mat,2,mean)
ssq2=apply(data2.mat,2,var)
ybar2=apply(data2.mat,2,mean)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=((ybar1-ybar2)-(mean1-mean2))/sqrt(spsq*(1/n1+1/n2))#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",T)),
xlab=paste(" T Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(Y)[1]-bar(Y)[2])-(mu[1]-mu[2]),S[p]*sqrt(frac(1,n[1])+frac(1,n[2])))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sdw=sd(w),fun="T")) # some output to use if needed
}
myTsim2(iter=10000)
```

	Use default values in the function with iter=10000 and use the output to make a histogram as before.

```{r}
myTsim2<-function(n1=10,n2=14,sigma1=3,sigma2=3,mean1=5,mean2=10,iter=1000,ymax=0.5,x=2,y=0.4,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ybar1= apply(data1.mat,2,mean)
ssq2=apply(data2.mat,2,var)
ybar2=apply(data2.mat,2,mean)
spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=((ybar1-ybar2)-(mean1-mean2))/sqrt(spsq*(1/n1+1/n2))#sigma1=sigma2,  Chi square stat
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",T)),
xlab=paste(" T Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(dt(x,n1+n2-2),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(T==frac((bar(Y)[1]-bar(Y)[2])-(mu[1]-mu[2]),S[p]*sqrt(frac(1,n[1])+frac(1,n[2])))) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sdw=sd(w),fun="T")) # some output to use if needed
}
T<-myTsim2(iter=10000)
hist(T$w)
```

## Task 6

```{r}

myFsim2<-function(n1=10,n2=14,sigma1=3,sigma2=2,mean1=5,mean2=10,iter=1000,ymax=0.9,x=6,y=0.5,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
#spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=ssq1*sigma2^2/(ssq2*sigma1^2) #
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",F)),
xlab=paste("F Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(df(x,n1-1,n2-1),xlim=c(0,6),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(F==frac(s[1]^2,s[2]^2)*frac(sigma[2]^2,sigma[1]^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="F")) # some output to use if needed
}
myFsim2(iter=10000)
```

$$

F = (\frac {S_{1}^{2}} {S_{2}^{2}}) (\frac {\sigma_{2}^{2}} {\sigma_{2}^{1}}) 

$$
Assumptions: F distributions with v1 = (n1-1) numerator degree of freedom and v2 = (n2-1) denominator degree of freedom. No additional assumptions are made.

o	Make four plots with different parameters.
	n_1=10,n_2=10,μ_1=5,μ_2=10,σ_1=σ_2=4,iter=1000
	n_1=20,n_2=10,μ_1=3,μ_2=5,σ_1=σ_2=10,iter=1000
	n_1=50,n_2=50,μ_1=5,μ_2=10,σ_1=σ_2=4,iter=10000
	n_1=80,n_2=50,μ_1=3,μ_2=5,σ_1=σ_2=10,iter=10000

Plot 1
```{r}
myFsim2<-function(n1=10,n2=10,sigma1=4,sigma2=4,mean1=5,mean2=10,iter=1000,ymax=0.9,x=6,y=0.5,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
#spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=ssq1*sigma2^2/(ssq2*sigma1^2) #
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",F)),
xlab=paste("F Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(df(x,n1-1,n2-1),xlim=c(0,6),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(F==frac(s[1]^2,s[2]^2)*frac(sigma[2]^2,sigma[1]^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="F")) # some output to use if needed
}
myFsim2(iter=10000,  xmax = 5)
```
PLot 2
```{r}

myFsim2<-function(n1=20,n2=10,sigma1=10,sigma2=10,mean1=3,mean2=5,iter=1000,ymax=0.9,x=6,y=0.5,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
#spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=ssq1*sigma2^2/(ssq2*sigma1^2) #
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",F)),
xlab=paste("F Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(df(x,n1-1,n2-1),xlim=c(0,6),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(F==frac(s[1]^2,s[2]^2)*frac(sigma[2]^2,sigma[1]^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="F")) # some output to use if needed
}
myFsim2(iter=10000)
```
PLot 3
```{r}

myFsim2<-function(n1=50,n2=50,sigma1=4,sigma2=4,mean1=5,mean2=10,iter=10000,ymax=0.9,x=6,y=0.5,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
#spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=ssq1*sigma2^2/(ssq2*sigma1^2) #
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",F)),
xlab=paste("F Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(df(x,n1-1,n2-1),xlim=c(0,6),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(F==frac(s[1]^2,s[2]^2)*frac(sigma[2]^2,sigma[1]^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="F")) # some output to use if needed
}
myFsim2(iter=10000, ymax = 2)
```

PLot 4
```{r}

myFsim2<-function(n1=80,n2=50,sigma1=10,sigma2=10,mean1=3,mean2=5,iter=10000,ymax=0.9,x=6,y=0.5,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
#spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=ssq1*sigma2^2/(ssq2*sigma1^2) #
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",F)),
xlab=paste("F Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(df(x,n1-1,n2-1),xlim=c(0,6),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(F==frac(s[1]^2,s[2]^2)*frac(sigma[2]^2,sigma[1]^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="F")) # some output to use if needed
}
myFsim2(iter=10000, ymax = 2)
```


o	Make a histogram from the function using default values.

```{r}
myFsim2<-function(n1=10,n2=14,sigma1=3,sigma2=2,mean1=5,mean2=10,iter=1000,ymax=0.9,x=6,y=0.5,...){
y1=rnorm(n1*iter,mean=mean1,sd=sigma1)# generate iter samples of size n1
y2=rnorm(n2*iter,mean=mean2,sd=sigma2)
data1.mat=matrix(y1,nrow=n1,ncol=iter,byrow=TRUE) # Each column is a sample size n1
data2.mat=matrix(y2,nrow=n2,ncol=iter,byrow=TRUE)
ssq1=apply(data1.mat,2,var) # ssq1 is s squared
ssq2=apply(data2.mat,2,var)
#spsq=((n1-1)*ssq1 + (n2-1)*ssq2)/(n1+n2-2) # pooled s squared
w=ssq1*sigma2^2/(ssq2*sigma1^2) #
hist(w,freq=FALSE, ylim=c(0,ymax), # Histogram with annotation
main=substitute(paste("Sample size = ",n[1]+n[2]," = ",n1+n2," statistic = ",F)),
xlab=paste("F Statistic",sep=""), las=1)
lines(density(w),col="Blue",lwd=3) # add a density plot
curve(df(x,n1-1,n2-1),xlim=c(0,6),add=TRUE,col="Red",lty=2,lwd=3) # add a theoretical curve
title=expression(F==frac(s[1]^2,s[2]^2)*frac(sigma[2]^2,sigma[1]^2)) #mathematical annotation -see ?plotmath
legend(x,y,c("Simulated","Theoretical"),col=c("Blue","Red"),lwd=4,lty=1:2,bty="n",title=title)# Legend #
invisible(list(w=w,summary=summary(w),sd=sd(w),fun="F")) # some output to use if needed
}
T<-myFsim2(iter=10000)
hist(T$w)
```

Task 7

```{r}
fire=read.csv("FIREDAM.csv")
usethis::use_data(fire)
```

